---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)
```

# fuRious

**Author:** [Mark Rieke](https://www.thedatadiary.net/about/)
**License:** [MIT](https://github.com/markjrieke/fuRious/blob/main/LICENSE)

<!-- badges: start -->
[![R-CMD-check](https://github.com/markjrieke/fuRious/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/markjrieke/fuRious/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## Overview

`{fuRious}` is a package for generating a family of movie titles based on the Fast & Furious series. This is a gag-package created alongside a submission for a lightening talk at [posit::conf(2023)](https://posit.co/conference/).

## Installation

This package is not released on CRAN. You can install from github:

```{r, eval=FALSE}
devtools::install_github("markjrieke/fuRious")
```

## Usage

The workhorse of the package is the function `generate_titles()`. By default, `generate_titles()` will recreate the titles from the Fast & Furious series.

```{r}
library(fuRious)

generate_titles()
```

You can also generate a new series of titles:

```{r}
generate_titles("star", "wars")
generate_titles("harry", "potter")
```

